Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-13 Paper.tex
Fix memory linear cost limit: 724B -> 704B
The "a" in the C_mem function is number of *words*.

If a * a >= 512, the cost will become non-linear.

1 word = 32 bytes

>>> bytes_used = 704
>>> a = int(math.ceil(float(bytes_used) / 32))
>>> a
22
>>> a * a >= 512
False

>>> bytes_used = 705
>>> a = int(math.ceil(float(bytes_used) / 32))
>>> a
23
>>> a * a >= 512
True

The cost is linear up to 704B.

Note also that $C_{\mathrm{mem}}$ is the memory cost function (the expansion function being the difference between the cost before and after). It is a polynomial, with the higher-order coefficient divided and floored, and thus linear up to 724B of memory used, after which it costs substantially more.

>>>>

Note also that $C_{\mathrm{mem}}$ is the memory cost function (the expansion function being the difference between the cost before and after). It is a polynomial, with the higher-order coefficient divided and floored, and thus linear up to 704B of memory used, after which it costs substantially more.
